Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-09 paper/main.tex
[issue 2.18] fifteen to fourteen

\item{Reflection:
We flip each image horizontally with a probability of 0.5 to exploit mirror symmetry. }
\item{Translation:
We also have translational symmetry in the images.
Given an image of size $48\times48$ pixels, we extract a random contiguous crop
of size $44\times44$.
Each cropping is equivalent to randomly shifting a $44\times44$ image by up to 4 pixels
vertically and/or horizontally. }
\item{Gaussian noise:
We introduce random Gaussian noise to each pixel values
by using a similar method to \cite{krizhevsky2012imagenet}. }
\end{itemize}
These data augmentation schemes add almost no computational cost,
as they are performed on the CPU while the GPU is training the ConvNets on images.

@@

We train two TPC models on the SDSS data set by using different sets of
attributes.
The first model, which we denote $\rmn{TPC}_{\rmn{phot}}$, is trained with
only nine photometric attributes:
the extinction-corrected model magnitudes in five bands
($u$, $g$, $r$, $i$, $z$)
and their corresponding colors
($u-g$, $g-r$, $r-i$, $i-z$).
The second model, which we denote $\rmn{TPC}_{\rmn{morph}}$, is trained with
the concentration parameter in each band in addition to the magnitudes and
colors, for a total of fifteen dimensions.
The concentration is defined as the difference between the
\sout{cmodel and}
\changed{
PSF magnitude (psfMag) and the composite model magnitude (cModelMag), \ie
}
$\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
The SDSS pipeline uses a parametric method based on the concentration,
an object is classified as a galaxy if $\rmn{concentration}>0.145$.
We find that the concentration is an excellent morphological feature
for star-galaxy separation, and including more morphological features
does not show noticeable improvement in performance.
The concentration is a good example of carefully handcrafted feature extraction;
we show in Section~\ref{sec:results_and_discussion}
that ConvNets do not require such feature engineering.

>>>>

\item{Reflection:
We flip each image horizontally with a probability of 0.5 to exploit mirror symmetry. }
\item{Translation:
We also have translational symmetry in the images.
Given an image of size $48\times48$ pixels, we extract a random contiguous crop
of size $44\times44$.
Each cropping is equivalent to randomly shifting a $44\times44$ image by up to 4 pixels
vertically and/or horizontally. }
\item{Gaussian noise:
We introduce random Gaussian noise to each pixel values
by using a similar method to \cite{krizhevsky2012imagenet}.}
\end{itemize}
These data augmentation schemes add almost no computational cost,
as they are performed on the CPU while the GPU is training the ConvNets on images.

@@

We train two TPC models on the SDSS data set by using different sets of
attributes.
The first model, which we denote $\rmn{TPC}_{\rmn{phot}}$, is trained with
only nine photometric attributes:
the extinction-corrected model magnitudes in five bands
($u$, $g$, $r$, $i$, $z$)
and their corresponding colors
($u-g$, $g-r$, $r-i$, $i-z$).
The second model, which we denote $\rmn{TPC}_{\rmn{morph}}$, is trained with
the concentration parameter in each band in addition to the magnitudes and
colors, for a total of
\changed{
fourteen
}
dimensions.
The concentration is defined as the difference between the
\sout{cmodel and}
\changed{
PSF magnitude (psfMag) and the composite model magnitude (cModelMag), \ie
}
$\rmn{concentration}\equiv\rmn{psfMag}-\rmn{cModelMag}$.
The SDSS pipeline uses a parametric method based on the concentration,
an object is classified as a galaxy if $\rmn{concentration}>0.145$.
We find that the concentration is an excellent morphological feature
for star-galaxy separation, and including more morphological features
does not show noticeable improvement in performance.
The concentration is a good example of carefully handcrafted feature extraction;
we show in Section~\ref{sec:results_and_discussion}
that ConvNets do not require such feature engineering.
